Draft Documents

### 2022-11-03 src/draft.Rmd
add gdp.pc (gdp per capita) to countries.csv and draft docs

1.  **country.code**: Country code\
2.  **country.name**: Country name\
3.  **year**: Year\
4.  **income**: Income class
    -   Low income (L)\
    -   Lower middle income (LM)\
    -   Upper middle income (UM)\
    -   High income (H)\
5.  **reg**: Region\
6.  **pov**: Poverty headcount ratio\
7.  **mpi**: Multidimensional Poverty Index\
8.  **edu.total**: Total expenditure on education (% of GDP)\
9.  **edu.pri**: Total expenditure on primary education (% of total education expenditure)\
10. **edu.sec**: Total expenditure on secondary education (% of total education expenditure)\
11. **edu.ter**: Total expenditure on tertiary education (% of total education expenditure)\
12. **hlth**: Total expenditure on health (% of GDP)\
13. **mil**: Total expenditure on military (% of GDP)\
14. **fdi**: Foreign Direct Investment\
15. **lbr.part**: Labour force participation (% of population ages 15+)\
16. **unemp**: Unemployment rate\
17. **pop.gwth.total**: Total population growth rate\
18. **pop.gwth.rural**: Total rural population growth rate\
19. **pop.gwth.urban**: Total urban population growth rate\
20. **gdp.dflt**: GDP deflator\
21. **gdr.eql**: Gender equality rating\
22. **gcf**: Gross Capital Formation\
23. **trade**: Trade = import + export (% of GDP)

@@

poverty.headcount <- importWDI("poverty.headcount.215dollar.csv", "pov")
mpi <- importWDI("mpi.csv", "mpi")
education.expenditure.total <- importWDI("total.education.expenditure.csv", "edu.total")
education.expenditure.primary <- importWDI("primary.education.expenditure.csv", "edu.pri")
education.expenditure.secondary <- importWDI("secondary.education.expenditure.csv", "edu.sec")
education.expenditure.tertiary <- importWDI("tertiary.education.expenditure.csv", "edu.ter")
health.expenditure <- importWDI("health.expenditure.csv", "hlth")
military.expenditure <- importWDI("military.expenditure.csv", "mil")
fdi <- importWDI("fdi.csv", "fdi")
labour.force.participation <- importWDI("labour.force.participation.csv", "lbr.part")
unemployment.rate <- importWDI("unemployment.csv", "unemp")
population.growth <- importWDI("population.growth.csv", "pop.gwth.total")
rural.population.growth <- importWDI("rural.population.growth.csv", "pop.gwth.rural")
urban.population.growth <- importWDI("urban.population.growth.csv", "pop.gwth.urban")
gdp.deflator <- importWDI("gdp.deflator.csv", "gdp.dflt")
gender.equality <- importWDI("gender.equality.csv", "gdr.eql")
gross.capital.formation <- importWDI("gross.capital.formation.csv", "gcf")
trade <- importWDI("trade.csv", "trade")
region.class <- importRegionClass("region.class.csv")
income.class <- importIncomeClass("income.class.csv")

@@

```{r}
# Rename countries in all data sets.
poverty.headcount <- poverty.headcount %>%
  mutate(country.name = correctName(country.name))
mpi <- mpi %>%
  mutate(country.name = correctName(country.name))
education.expenditure.total <- education.expenditure.total %>%
  mutate(country.name = correctName(country.name))
education.expenditure.primary <- education.expenditure.primary %>%
  mutate(country.name = correctName(country.name))
education.expenditure.secondary <- education.expenditure.secondary %>%
  mutate(country.name = correctName(country.name))
education.expenditure.tertiary <- education.expenditure.tertiary %>%
  mutate(country.name = correctName(country.name))
health.expenditure <- health.expenditure %>%
  mutate(country.name = correctName(country.name))
military.expenditure <- military.expenditure %>%
  mutate(country.name = correctName(country.name))
fdi <- fdi %>%
  mutate(country.name = correctName(country.name))
labour.force.participation <- labour.force.participation %>%
  mutate(country.name = correctName(country.name))
unemployment.rate <- unemployment.rate %>%
  mutate(country.name = correctName(country.name))
population.growth <- population.growth %>%
  mutate(country.name = correctName(country.name))
rural.population.growth <- rural.population.growth %>%
  mutate(country.name = correctName(country.name))
urban.population.growth <- urban.population.growth %>%
  mutate(country.name = correctName(country.name))
gdp.deflator <- gdp.deflator %>%
  mutate(country.name = correctName(country.name))
gender.equality <- gender.equality %>%
  mutate(country.name = correctName(country.name))
gross.capital.formation <- gross.capital.formation %>%
  mutate(country.name = correctName(country.name))
trade <- trade %>%
  mutate(country.name = correctName(country.name))
region.class <- region.class %>%
  mutate(country.name = correctName(country.name))
income.class <- income.class %>%
  mutate(country.name = correctName(country.name))
```

@@

```{r, message = F}
countries <- poverty.headcount %>% 
  # We used a full join here so we can conduct a separate analysis on mpi later
  full_join(mpi, by = c("country.name", "country.code", "year")) %>%
  left_join(income.class, c("country.name", "country.code", "year")) %>% 
  left_join(region.class, by = "country.name") %>%
  left_join(education.expenditure.total, by = c("country.name", "country.code", "year")) %>%
  left_join(education.expenditure.primary, by = c("country.name", "country.code", "year")) %>%
  left_join(education.expenditure.secondary, by = c("country.name", "country.code", "year")) %>%
  left_join(education.expenditure.tertiary, by = c("country.name", "country.code", "year")) %>%
  left_join(health.expenditure, by = c("country.name", "country.code", "year")) %>%
  left_join(military.expenditure, by = c("country.name", "country.code", "year")) %>%
  left_join(fdi, by = c("country.name", "country.code", "year")) %>%
  left_join(labour.force.participation, by = c("country.name", "country.code", "year")) %>%
  left_join(unemployment.rate, by = c("country.name", "country.code", "year")) %>%
  left_join(population.growth, by = c("country.name", "country.code", "year")) %>%
  left_join(rural.population.growth, by = c("country.name", "country.code", "year")) %>%
  left_join(urban.population.growth, by = c("country.name", "country.code", "year")) %>%
  left_join(gdp.deflator, by = c("country.name", "country.code", "year")) %>%
  left_join(gender.equality, by = c("country.name", "country.code", "year")) %>%
  left_join(gross.capital.formation, by = c("country.name", "country.code", "year")) %>%
  left_join(trade, by = c("country.name", "country.code", "year")) %>% 
  # filter special groups
  filter(!(country.name %in% spec.reg))
```

@@

## 2.3. Descriptive Analytics (To be done)

>>>>

1.  **country.code**: Country code\
2.  **country.name**: Country name\
3.  **year**: Year\
4.  **income**: Income class
    -   Low income (L)\
    -   Lower middle income (LM)\
    -   Upper middle income (UM)\
    -   High income (H)\
5.  **reg**: Region\
6.  **pov**: Poverty headcount ratio\
7.  **mpi**: Multidimensional Poverty Index\
8.  **edu.total**: Total expenditure on education (% of GDP)\
9.  **edu.pri**: Total expenditure on primary education (% of total education expenditure)\
10. **edu.sec**: Total expenditure on secondary education (% of total education expenditure)\
11. **edu.ter**: Total expenditure on tertiary education (% of total education expenditure)\
12. **hlth**: Total expenditure on health (% of GDP)\
13. **mil**: Total expenditure on military (% of GDP)\
14. **fdi**: Foreign Direct Investment\
15. **lbr.part**: Labour force participation (% of population ages 15+)\
16. **unemp**: Unemployment rate\
17. **pop.gwth.total**: Total population growth rate\
18. **pop.gwth.rural**: Total rural population growth rate\
19. **pop.gwth.urban**: Total urban population growth rate\
20. **gdp.dflt**: GDP deflator\
21. **gdr.eql**: Gender equality rating\
22. **gcf**: Gross Capital Formation\
23. **trade**: Trade = import + export (% of GDP)
24. **gdp.pc**: GDP per capita (current US$)

@@

poverty.headcount <- importWDI("poverty.headcount.215dollar.csv", "pov")
mpi <- importWDI("mpi.csv", "mpi")
education.expenditure.total <- importWDI("total.education.expenditure.csv", "edu.total")
education.expenditure.primary <- importWDI("primary.education.expenditure.csv", "edu.pri")
education.expenditure.secondary <- importWDI("secondary.education.expenditure.csv", "edu.sec")
education.expenditure.tertiary <- importWDI("tertiary.education.expenditure.csv", "edu.ter")
health.expenditure <- importWDI("health.expenditure.csv", "hlth")
military.expenditure <- importWDI("military.expenditure.csv", "mil")
fdi <- importWDI("fdi.csv", "fdi")
labour.force.participation <- importWDI("labour.force.participation.csv", "lbr.part")
unemployment.rate <- importWDI("unemployment.csv", "unemp")
population.growth <- importWDI("population.growth.csv", "pop.gwth.total")
rural.population.growth <- importWDI("rural.population.growth.csv", "pop.gwth.rural")
urban.population.growth <- importWDI("urban.population.growth.csv", "pop.gwth.urban")
gdp.deflator <- importWDI("gdp.deflator.csv", "gdp.dflt")
gender.equality <- importWDI("gender.equality.csv", "gdr.eql")
gross.capital.formation <- importWDI("gross.capital.formation.csv", "gcf")
trade <- importWDI("trade.csv", "trade")
region.class <- importRegionClass("region.class.csv")
income.class <- importIncomeClass("income.class.csv")
gdp.pc <- importWDI("gdp.pc.csv", "gdp.pc")

@@

```{r}
# Rename countries in all data sets.
poverty.headcount <- poverty.headcount %>%
  mutate(country.name = correctName(country.name))
mpi <- mpi %>%
  mutate(country.name = correctName(country.name))
education.expenditure.total <- education.expenditure.total %>%
  mutate(country.name = correctName(country.name))
education.expenditure.primary <- education.expenditure.primary %>%
  mutate(country.name = correctName(country.name))
education.expenditure.secondary <- education.expenditure.secondary %>%
  mutate(country.name = correctName(country.name))
education.expenditure.tertiary <- education.expenditure.tertiary %>%
  mutate(country.name = correctName(country.name))
health.expenditure <- health.expenditure %>%
  mutate(country.name = correctName(country.name))
military.expenditure <- military.expenditure %>%
  mutate(country.name = correctName(country.name))
fdi <- fdi %>%
  mutate(country.name = correctName(country.name))
labour.force.participation <- labour.force.participation %>%
  mutate(country.name = correctName(country.name))
unemployment.rate <- unemployment.rate %>%
  mutate(country.name = correctName(country.name))
population.growth <- population.growth %>%
  mutate(country.name = correctName(country.name))
rural.population.growth <- rural.population.growth %>%
  mutate(country.name = correctName(country.name))
urban.population.growth <- urban.population.growth %>%
  mutate(country.name = correctName(country.name))
gdp.deflator <- gdp.deflator %>%
  mutate(country.name = correctName(country.name))
gender.equality <- gender.equality %>%
  mutate(country.name = correctName(country.name))
gross.capital.formation <- gross.capital.formation %>%
  mutate(country.name = correctName(country.name))
trade <- trade %>%
  mutate(country.name = correctName(country.name))
region.class <- region.class %>%
  mutate(country.name = correctName(country.name))
income.class <- income.class %>%
  mutate(country.name = correctName(country.name))
gdp.pc <- gdp.pc %>%
  mutate(country.name = correctName(country.name))
```

@@

```{r, message = F}
countries <- poverty.headcount %>% 
  # We used a full join here so we can conduct a separate analysis on mpi later
  full_join(mpi, by = c("country.name", "country.code", "year")) %>%
  left_join(income.class, c("country.name", "country.code", "year")) %>% 
  left_join(region.class, by = "country.name") %>%
  left_join(education.expenditure.total, by = c("country.name", "country.code", "year")) %>%
  left_join(education.expenditure.primary, by = c("country.name", "country.code", "year")) %>%
  left_join(education.expenditure.secondary, by = c("country.name", "country.code", "year")) %>%
  left_join(education.expenditure.tertiary, by = c("country.name", "country.code", "year")) %>%
  left_join(health.expenditure, by = c("country.name", "country.code", "year")) %>%
  left_join(military.expenditure, by = c("country.name", "country.code", "year")) %>%
  left_join(fdi, by = c("country.name", "country.code", "year")) %>%
  left_join(labour.force.participation, by = c("country.name", "country.code", "year")) %>%
  left_join(unemployment.rate, by = c("country.name", "country.code", "year")) %>%
  left_join(population.growth, by = c("country.name", "country.code", "year")) %>%
  left_join(rural.population.growth, by = c("country.name", "country.code", "year")) %>%
  left_join(urban.population.growth, by = c("country.name", "country.code", "year")) %>%
  left_join(gdp.deflator, by = c("country.name", "country.code", "year")) %>%
  left_join(gender.equality, by = c("country.name", "country.code", "year")) %>%
  left_join(gross.capital.formation, by = c("country.name", "country.code", "year")) %>%
  left_join(trade, by = c("country.name", "country.code", "year")) %>% 
  left_join(gdp.pc, by = c("country.name", "country.code", "year")) %>% 
  # filter special groups
  filter(!(country.name %in% spec.reg))
```

@@

## 2.3. Descriptive Analytics
Distribution of the predicted variable `pov`
```{r}
ggplot(countries, aes(x = pov)) +
  geom_bar()
```
